D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-24 ootavacuous.tex
Self-review of Figure 6 text
Better explain atemporal coe.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Figure~\ref{fig:Propagation Delay and Temporal Properties of coe, fre, and rfe}
shows how the temporal properties of coe, fre, and rfe are explained
by propagation delay.
The upper portion of the figure shows an atemporal coe, in which
CPU~0 stores 1 to \co{x} after CPU~3 stores 2 to \co{x}, but
the ordering of the stores is decided after the fact.
In this case, the value of 2 from CPU~3's store overwrites the value
of 1 from CPU~0's store, despite the fact that CPU~0's store
happened later in time.
The middle portion of the figure shows an atemporal fre, in which
CPU~3's load obtains the old value of zero from \co{x} despite
having executed long after CPU~0's store, courtesy of the fact
that the new value of \co{x} had not yet propagated to CPU~3.
The lower portion of the figure shows a temporal rfe.
Because CPU~3's load cannot obtain the value stored by CPU~0 until
after that value has propagated to CPU~3, the fact that CPU~3 obtains
the new value implies that the load was executed after the store.

>>>>

Figure~\ref{fig:Propagation Delay and Temporal Properties of coe, fre, and rfe}
shows how propagation delay explains the temporal properties of coe,
fre, and rfe.
The upper portion of the figure shows an atemporal coe, in which
CPU~0 stores 1 to \co{x} after CPU~3 stores 2 to \co{x}, but
the ordering of the stores is decided after the fact.
In this case, the value of 2 from CPU~3's store overwrites the value
of 1 from CPU~0's store, despite the fact that CPU~0's store
happened later in time.
One way that this could happen is that the cache line containing
\co{x} happened to arrive at CPU~3 before arriving at CPU~0.
A more fanciful explanation is that both values arrived at the
interconnect at the saem time, and the interconnect made an
arbitrary choice between the two.
Either way, the end result is that an earlier store can overwrite
a later store.

The middle portion of the figure shows an atemporal fre, in which
CPU~3's load obtains the old value of zero from \co{x} despite
having executed long after CPU~0's store, courtesy of the fact
that the new value of \co{x} had not yet propagated to CPU~3.

The lower portion of the figure shows a temporal rfe.
Because CPU~3's load cannot obtain the value stored by CPU~0 until
after that value has propagated to CPU~3, the fact that CPU~3 obtains
the new value implies that the load was executed after the store.
